Title Goes Here

### 2021-04-06 analysis/paper/shceof.Rmd
Amplía el epígrafe del histograma.
#8
Más histograma
(#8)

\textcolor{red}{(Lo del histograma habría que explicarlo con un pocoo más detalle porque no es tan trivial. Primero decir para qué se hace, qué se hace exactamente y después recien decir cuál es el resultado y qué información aporta)}

The reason that the EOF analysis arrives to this optimal separation is that the Imaginary cEOF is the most common phase (either negative or positive)

@@

(ref:phase-histogram-cap) Histogram showing phase distribution of EOF2 for the period 1979 -- 2019. \textcolor{red}{(También ampliar)}

```{r phase-histogram, fig.cap = "(ref:phase-histogram-cap)", fig.width=width_column*.8, fig.height=2.5}
N <- nrow(cut(ceof$eof[[1]], 2)$left)
cut(ceof$eof[[1]], 2)$left %>% 
  .[, arg := Arg(hgt)] %>% 
  .[, w := Mod(hgt)/mean(Mod(hgt))] %>% 
  qwrap(arg = c(-pi, pi) ~  c(-pi - 1/4*pi, pi - 1/4*pi)) %>% 
  ggplot(aes(arg)) +
  geom_histogram(binwidth = 90*pi/180, center = 0, color = "black", fill = "gray70") +
  annotate("text",
           label = c("- Real", "- Imaginary", "+ Real", "+ Imaginary"),
           color = "black", size = 3,
           y = 0.5, x = c(-pi, -pi/2, 0, pi/2), angle = 90, hjust = 0) +
  geom_rug() +
  scale_y_continuous("Number of years", 
                     sec.axis = sec_axis(~.x/N, 
                                         name = "Proportion of years", 
                                         labels = scales::percent)) +
  scale_x_continuous("Phase",
                     breaks = seq(-pi - 1/4*pi, pi - 1/4*pi, by = 90*pi/180),
                     labels = function(x) paste0(round(x*180/pi, 5), "º")) 
```

>>>>

@@

(ref:phase-histogram-cap) Histogram of phase distribution of cEOF2 for the period 1979 -- 2019. Bins are centred at 90º, 0º, -90º, -180º with a binwidth of 90º.

```{r phase-histogram, fig.cap = "(ref:phase-histogram-cap)", fig.width=width_column*.8, fig.height=2.5}
N <- nrow(cut(ceof$eof[[1]], 2)$left)
cut(ceof$eof[[1]], 2)$left %>% 
  .[, arg := Arg(hgt)] %>% 
  .[, w := Mod(hgt)/mean(Mod(hgt))] %>% 
  qwrap(arg = c(-pi, pi) ~  c(-pi - 1/4*pi, pi - 1/4*pi)) %>% 
  ggplot(aes(arg)) +
  geom_histogram(binwidth = 90*pi/180, center = 0, size = 0.2,
                 color = "black", fill = "gray70") +
  annotate("text",
           label = c("- Real", "- Imaginary", "+ Real", "+ Imaginary"),
           color = "black", size = 3,
           y = 0.5, x = c(-pi, -pi/2, 0, pi/2), angle = 90, hjust = 0) +
  geom_rug() +
  scale_y_continuous("Number of years", 
                     sec.axis = sec_axis(~.x/N, 
                                         name = "Proportion of years", 
                                         labels = scales::percent)) +
  scale_x_continuous("Phase", trans = scales::reverse_trans(),
                     breaks = seq(-pi - 1/4*pi, pi - 1/4*pi, by = 45*pi/180),
                     labels = function(x) paste0(round(x*180/pi, 5), "º")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
